Ornaments as indicators of social changes and cultural practices in northeastern Taiwan before and after European colonial period

### 2019-12-10 analysis/paper/paper.Rmd
udpates c14 dating data to include more samples

The chronology of Kiwulan can be divided into two phases represented by a upper component (1400-1900 AD) and a lower component (700-1200 AD) separated by a sterile. This chronology is based on the stratigraphy and a series of 32 radiocarbon dates previously published by @Chen2007. The relationship between upper component and lower component is still under debate and the sterile might result from dry weather according to pollen analyses [@Lin2015; @Chiu2004; @Chen2007]. This paper focuses on the upper component covering a sequence spanning pre-European contact, European presence, and Chinese presence. Previous researches divided the upper component into six layers spanning from the 14th century to the 19th century with hundred year intervals according to the radiocarbon dates, excavation depth, consistency of contexts, and types of diagnostic porcelains such as blue and white porcelains [@Hsieh2009; @Wang2011]. To answer our research question, we re-examined and assigned previous layers to a new chronology with three episodes of time: pre-European period, European period, and Chinese period to indicate the dominant foreign influence and cultural interaction for different time periods.

@@

# have a look at the output
summary(kw_dates_with_error_calibrated)
par(mfrow = c(2, 3))
plot(kw_dates_with_error_calibrated)

# we can combine all the calibrated dates into a single plot, like this
kw_ages_densities <- 
  with(kw_dates_with_error,
       BchronDensity(
         ages = rce,
         ageSds = se,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))
       ))

>>>>

The chronology of Kiwulan can be divided into two phases represented by a upper component (1400-1900 AD, 600-100 BC) and a lower component (700-1200 AD, 1200-800 BC) separated by a sterile spanning 150 years according to . This chronology is based on the stratigraphy and a series of 32 radiocarbon dates previously published by @Chen2007. The relationship between upper component and lower component is still under debate and the sterile might result from dry weather according to pollen analyses [@Lin2015; @Chiu2004; @Chen2007]. This paper focuses on the upper component covering a sequence spanning pre-European contact, European presence, and Chinese presence. Previous researches divided the upper component into six layers spanning from the 14th century to the 19th century with hundred year intervals according to the radiocarbon dates, excavation depth, consistency of contexts, and types of diagnostic porcelains such as blue and white porcelains [@Hsieh2009; @Wang2011]. To answer our research question, we re-examined and assigned previous layers to a new chronology with three episodes of time: pre-European period, European period, and Chinese period to indicate the dominant foreign influence and cultural interaction for different time periods.

@@

# have a look at the output
par(mfrow = c(2, 3))
plot(kw_dates_with_error_calibrated)

# we can combine all the calibrated dates into a single plot, like this
kw_ages_densities <- 
  with(kw_dates_with_error,
       BchronDensity(
         ages = rce,
         ageSds = se,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))
       ))
invisible(dev.off())
